### 2017-11-15 Risk analysis/Text/Layout/Layout/chapter3_results.tex
Working on 3D results text

		\section{3D geological model results}
		- first: MC simulation of only prior uncertainty error propagation to generate a prior reference model
		- second: Bayesian inference using only thickness likelihoods
		- third: Bayesian inference including SSF likelihood
		- last test: BI using only SSF likelihood

		\subsection{Prior model}
		\begin{figure}[h]
			\centering
			\includegraphics[width=1\textwidth]{Figures/M_prior}
			\caption{....}\label{fig:M_prior}
		\end{figure}

		\subsection{Posterior model I}
		\begin{figure}[p!]
			\centering
			\includegraphics[width=1\textwidth]{Figures/ML1}
			\caption{....}\label{fig:ML1}
		\end{figure}

>>>>

		\section{3D geological model results}
		In the following, results from applying the methods on the artificial 3D structural model are presented. Several representative examples of posterior models based on the use of different likelihoods are referenced to the original prior model. The following measures are central to the comparison of simulation results: (1) information entropy, (2) occurrence of trap control mechanisms, (3) resulting recoverable oil volumes and (3) consequent realization of expected losses and related Bayes actions (i.e. decisions).

		\subsection{Prior model}
		To generate a set of reference results, a prior model was first generated by running a simple simulation of Monte Carlo sampling and error propagation regarding only the uncertainty of prior parameters. No likelihood functions were included in this prior model. Prior parameter uncertainties were chosen to be identical for all models, prior and posteriors.
		\begin{table}[h]
		\begin{tabular}{lrrr} 
			\toprule
			(a) Uncertainty: layer boundaries $z$-position (normal distributions)\\  
			\midrule 
			Formation bottom & $\mu$ [m] & $\sigma$ [m]\\ 
			\midrule 
			Overlying & 0 & 40 \\
			Sandstone 2 & 0 & 60 \\
			Shale (Seal) & 0 & 80\\ 
			Sandstone 1 (Reservoir) & 0 & 100 \\
			\bottomrule
			\toprule
			(b) Uncertainty: normal fault offset (skew normal distribution)\\
			\midrule
			Fault side & $\mu$ [m] & $\sigma$ [m] & $\alpha$\\
			\midrule
			Hanging wall offset & 0 & -~150 & -~2\\
			\bottomrule 
		\end{tabular}
		\caption{Prior parameter uncertainties defined by distributions with respective means $\mu$, standard deviations $\sigma$ and shape factor $\alpha$, as used in all models. Uncertainties about the position of layer interfaces (a) are implemented by drawing values from normal distributions. All points belonging to one layer are assigned one shared distribution. Drawn values are added or subtracted respectively from the originally defined $z$-positional values. The offset uncertainty (b) is based on a skew normal distribution that affects all positional points in the hanging wall.}
		\label{tab:3D_prior_parameters}
		\end{table}
			\includegraphics[width=1\textwidth]{Figures/M_prior}
			\caption{Recoverable oil volumes probability distribution for the prior model (a) and respective realization of the custom loss function (b).}\label{fig:M_prior}
		The nature of the prior uncertainties is reflected by the visualization using information entropy (see Figure \ref{fig:ML1} (a)). High entropies are found at and near the possible locations of layer boundaries. This effect is amplified by the offset uncertainty in the footwall, where the highest information entropies are found.\\
		Regarding the different mechanisms of maximum trap volume control, it can be observed (see Figure \ref{fig:ML1} (c)) that all four relevant mechanisms occurred. The dominant factor is the anticlinal spill point (labeled "SPILL POINT"), accounting for more than 60\% of model realizations. It is followed by cross-fault leakage due to juxtaposition with formations underlying ("LEAK UNDER", ~20\%) and formations overlying ("LEAK OVER", ~13\%) the seal in the footwall. Leakage due to stratigraphical connections to seal-overlying units ("STRAT"), i.e. stratigraphical breaches of the seal, were registered to be decisive in only about 3\% of realizations. A satisfactory reliability of model algorithms and computation is indicated by the lack of unrecognized mechanisms (labeled "UNCLEAR", see Figure \ref{fig:ML1} (c)).\\
		Recoverable oil volumes were calculated for each model iteration and plotted as a probability distribution in Figure \ref{fig:M_prior} (a). It can clearly be seen that while a large portion of the distribution is found in highly positive volumes, forming a normal distribution shape around 3.8 million $m³$, there also a high probability of complete failure, i.e. a maximum trap volume of zero. This results in a bimodal characterization, with low probability of the $ROV$ to be found between zero and three million $m³$.\\
		Consequently, applying the custom loss function on this distribution results in divergent Bayes actions for the different risk-affine actors (see Figure \ref{fig:M_prior} (b)). Although all actors find their estimates to be positive, only the risk-neutral to risk-friendliest actors come close to the positive mode of the distribution. Risk-averse individuals bid on significantly lower estimates. It can also be observed, that expected losses seem to be generally lower for risk-affine actors. The different Bayes actions have apparently been torn apart by the bimodality of the $ROV$ probability distribution.

		\subsection{Posterior model I}
		\begin{table}[h]
			\centering
			\begin{tabular}{lrr} 
				\toprule
				Model I - Likelihoods: layer thicknesses (normal distributions)\\  
				\midrule 
				Formation & $\mu$ [m] & $\sigma$ [m]\\ 
				\midrule 
				Sandstone 2 & 150 & 30 \\
				Shale (Seal) & 350 & 30\\ 
				Sandstone 1 (Reservoir) & 250 & 30 \\
				\bottomrule
			\end{tabular}
			\caption{Layer thickness likelihoods determined by normal distributions as used for posterior model I.}
			\label{tab:ML1_likelihoods}
		\end{table}
		For the simulation of this first posterior model, thickness likelihoods for the three central layers were defined (see Table \ref{tab:ML1_likelihoods}).
		\begin{figure}[p!]
			\centering
			\includegraphics[width=1\textwidth]{Figures/ML1}
			\caption{....}\label{fig:ML1}
		\end{figure}
